---
title: "HW 9 613"
output:
  word_document: default
  html_document: default
---


###David Saff

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#install.packages("tidycensus")
library(tidycensus)
library(tidyverse)
library(dplyr)
library(ggplot2)
```

```{r}
census_api_key("f31f868a4d1d66ed9f67a3c675496f35e2f7506b")
install = TRUE
```

2) Using ACS census data from 2015, show and use R code to do the following:
a) Produce a tibble that shows the median income estimates and the margin of errors for white males in the counties of California.  The required variable code starts with the characters BO1OO1. Use the table to find the other characters.
```{r}
v15 <- load_variables(2015, "acs5", cache = TRUE)

#View(v15)
```

```{r}

CA <- get_acs(geography = "county", 
              variables = c(medincome = "B01001A_011"), 
              state = "CA", 
              year = 2015)
CA
```

b) Use a dplyr functions to change your table of part a so that it reflects estimates that are greater than $30,000 dollars and list the estimates in descending order.
```{r}

CA %>%
  filter(estimate > 30000) %>%
  arrange(desc(estimate)) -> CA2
CA2
```
c) Using the tibble that you produced in part b, use and show R code that will show the county that has a median income estimate of 51644 and a margin of error of 667.
```{r}
CA2 %>%
  filter(estimate == 51644) %>%
  filter(moe == 667)
```

d) Use and show ggplot coding that will produce the following boxplot for the data that you generated for part b.
```{r}
CA2 %>%
  ggplot(aes(x = estimate, fill = "red")) + geom_boxplot()  + theme(legend.position = "none") 
  
```
e) Use and show R code that will produce the following graph for the data generated in part b

```{r}
CA2 %>%
  mutate(NAME = gsub(" County, California", "", NAME)) %>%
  ggplot(aes(x = estimate, y = reorder(NAME, estimate))) +  
  geom_errorbar(aes(xmin = estimate-moe, xmax = estimate + moe)) +
  geom_point(color = "blue", size = 3) +
  labs(title = "Median Income For White Males by County",
       subtitle = "2014-2018 American Community Survey",
       y = "",
       x = "ACS estimate (bars represent margin of error)")


```

